---
title: "STAA 566 HW2 - Dynamic Figure"
author: "Tuul Purevjav"
date: "2/17/2022"
output: html_document
knit: (function(input_file, encoding) {
  out_dir <- 'docs';
  rmarkdown::render(input_file,
 encoding=encoding,
 output_file=file.path(dirname(input_file), out_dir, 'index.html'))})
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
My husband investigates stock trading as a side interest. He wanted to see a figure that shows a strategy commonly referred to as "golden cross and death cross." For this assignment, I visualized that strategy. I found my market data from Kaggle.com at https://www.kaggle.com/paultimothymooney/stock-market-data, and chose Amazon stock as my subject.  
For a given stock, the daily price crossing over 30-day (for example) moving average provides an entry price for buying a stock. The daily price crossing under 30-day average provides an exit price for selling a stock. These entry and exit prices provide strategy for taking profit more consistently than taking losses. I made a 30-day simple moving average. Typically, it's up to the trader to choose how many days, it could be as many as 200 days I believe. Statistically, this is a trailing indicator that takes advantage of the historical data to predict future entry and exit prices to maximize profit.

```{r message = FALSE}
library(readr)
library(lubridate)
library(dplyr)
library(tidyr)
library(xts)
library(dygraphs)
```

```{r}
shares <- read_csv("AMZN.csv", show_col_types = FALSE)
shares <-shares %>% 
  # setting Date column as a date object in "dmy" format
  mutate(Date = as.Date(parse_date_time(Date,"dmy")))
```

```{r}
# the market data is from 1997-05-15 to 2022-02-14
# limit to date range greater than "2019-12-31" 
shares <-shares %>% 
  filter(Date >= as.Date("2019-12-31"))
# get columns relevant for the plot
shares <-shares %>% 
 select(Date, Close)
```

Here, I'm taking the daily price and the average of 30 day price to see where they cross (intersect) in the plot.
```{r}
# arrange by date
# create daily price and 30 day lag variables
shares <- shares %>%
  arrange(Date) %>%
  mutate(price_1day  = Close,
         price_30day  = zoo::rollmean(price_1day, 30, fill=NA, align="right"))
shares <- shares %>% 
  select(Date, price_1day, price_30day) %>%
  drop_na()
```

Since I want to show time series data in my figure, I used `dygraphs`.
```{r}
# make an xts object
xts_1_30day <- xts::xts(x = shares %>% select(price_1day, price_30day),  # data (y axis)
                     order.by = shares %>% pull(Date))                # date (x axis)
p_shares_dy <- dygraph(xts_1_30day) %>%
  dySeries("price_1day", label = "1 Day Price") %>%
  dySeries("price_30day", label = "30 Day Price")  %>%
  dyRangeSelector()
p_shares_dy
```

